How has the Brazilian Amazon been constructed as a problem? An analysis of presidential speeches since 1985

### 2022-04-04 Draft_April_2022/Full_draft_20220401.qmd
Added modelling final file and a first attempt at the model

knitr::opts_chunk$set(include = FALSE)
library(tidyverse)
library(tidyr)
library(skimr)
library(scales)
library(RColorBrewer)
library(kableExtra)
library(nnet)

@@

>>>>

knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(ggplot2)
library(tidyr)
library(skimr)
library(scales)
library(RColorBrewer)
library(kableExtra)
library(nnet)
library(stargazer)

@@

```{r}
ama_model <- ama %>% 
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = as.factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
                                      mixed_type == '0_0_0_0' ~ "Other",
                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
                                            mixed_type) ~ "Other Types"))) %>% 
  mutate(mx_cat2 = case_when(!grepl("Pure Economic Integration|Pure Social Development|Pure Conservation|Pure Sovereignty|^Other$", mx_cat) ~ "Mixed Types"),
         mx_cat2 = as.factor(ifelse(is.na(mx_cat2), paste0(mx_cat), mx_cat2)),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0)) %>% 
  filter(location_cat != "Non Identified")  # remove the 3 obs
# get deforestation yearly (year before) - load data and merge
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>% # yearly deforestation rates only come out the year after
  rename(def_year = `area km²`)
ama_model <- dplyr::left_join(ama_model, amazon_def_year, by = "year") # merge
# inflation rates per year Brazil (average for year - but could be change)
AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds") # source world bank
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
# model
model <- multinom(mx_cat2 ~ location_cat + election_year + def_year + AAI, data = ama_model)
# get a nice table
stargazer::stargazer(model, type="text", add.lines = nrow(model$residuals), title = "Amazon Contructions by Location",
                     covariate.labels = c("Brasilia", "International", "Non-AM State",
                                          "Election Year", "Deforastion (year)", "Avg. Inflation (year)"),
                     column.labels = c("Other", "Conservation", "Economic Integration",
                                       "Social Development", "Sovereignty"),
                     dep.var.labels.include = FALSE)
```
